### 2018-10-31 Paper/Manuscript.tex
Swapped the order of my institutions
Minor corrections to paper More added to the talk

\author{Sarp Akcay}
\affiliation{School of Mathematics \& Statistics, University College Dublin, Belfield, Dublin 4, Ireland}
\affiliation{Theoretisch-Physikalisches Institut, Friedrich-Schiller-Universit{\"a}t Jena, 07743, Jena, Germany}
%\date{\today}

@@

Let us now turn our attention to the GWs generated by the inspiral.
These are tensorial perturbations propagating at the speed of light in flat (Minkowski) spacetime.
In the so-called wave zone, defined by the condition $ \lambda= c/f \ll D$, where $\lambda$ is the GW wavelength and $D$ is the distance to the GW source, 
these tensor modes satisfy the flat spacetime sourceless wave equation. %$\Box\bar{h}_{\mu\nu} = 0$.
%meaning that we are considering the solutions far from the GW source, 
%
It can further be shown that there exist only two radiative degrees of freedom (cf. Sec.~1.2 of Ref.~\cite{Maggiore}) which physically manifest themselves as two independent polarization amplitudes $h_+$ and $h_\times$ of the GWs 
This fact is most easily demonstrated in the so-called transverse-traceless gauge (cf. Sec.~2.1 of Ref.~\cite{Flanagan:2005yc}),
 but is a gauge-invariant consequence of linearized vacuum solutions. %when interacting with masses away from the source.

@@

\item {\it Truncating the inspiral at the Schwarzschild ISCO.}

@@

Therfore, letting $f =2f_K= 1\,\text{Hz}$, i.e., 

@@

\f{\dot\Omega}{\Omega^2} = \f{96}{5} \f{(G M_c)}{c^5}^{5/3}\Omega^{5/3} \ll 1 \label{eq:omega_dot_over_omegasq}

@@

This expression yields $\dot{\Omega}/\Omega^2\approx 5.5\times 10^{-4}$ at $f=100\,$Hz, which, as shown above, is a few seconds

>>>>

\author{Sarp Akcay}
\affiliation{Theoretisch-Physikalisches Institut, Friedrich-Schiller-Universit{\"a}t Jena, 07743, Jena, Germany}
\affiliation{School of Mathematics \& Statistics, University College Dublin, Belfield, Dublin 4, Ireland}
%\date{\today}

@@

Let us now turn our attention to the GWs generated by the inspiral.
These are tensorial perturbations propagating at the speed of light in flat (Minkowski) spacetime.
In the so-called wave zone, defined by the condition $ \lambda= c/f \ll D$, where $\lambda$ is the GW wavelength and $D$ is the distance to the GW source, 
these tensor modes satisfy the flat spacetime sourceless wave equation. %$\Box\bar{h}_{\mu\nu} = 0$.
%meaning that we are considering the solutions far from the GW source, 
%
It can further be shown that there exist only two radiative degrees of freedom (cf. Sec.~1.2 of Ref.~\cite{Maggiore}) which physically manifest themselves as two independent polarization amplitudes $h_+$ and $h_\times$ of the GWs. 
This fact is most easily demonstrated in the so-called transverse-traceless gauge (cf. Sec.~2.1 of Ref.~\cite{Flanagan:2005yc}),
 but is a gauge-invariant consequence of linearized vacuum solutions. %when interacting with masses away from the source.

@@

\item {\it Terminating the inspiral at the Schwarzschild ISCO.}

@@

Letting $f =2f_K= 1\,\text{Hz}$, i.e., 

@@

\f{|\dot\Omega|}{\Omega^2} = \f{96}{5} \f{(G M_c)}{c^5}^{5/3}\Omega^{5/3} \ll 1 \label{eq:omega_dot_over_omegasq}

@@

This expression yields $|\dot{\Omega}|/\Omega^2\approx 5.5\times 10^{-4}$ at $f=100\,$Hz, which, as shown above, is a few seconds

### 2018-10-31 Sabanci_talk/Sabanci_talk.tex
Minor corrections to paper More added to the talk

@@

\begin{frame}{Motivation: Multi-messenger Astronomy}
\begin{itemize}
 \item \emph{Multi}: two fundamentally different waves from common events.
 \item[]\quad Gravitational waves (GWs): ``hearing''  the universe.
 \item[]\quad Electromagnetic waves (EWs): ``seeing'' the universe.
 \item GW170817-GRB170817A-AT2017gfo: the ``event'' \\
 \quad inspiral + merger of two neutron stars (GWs) \\
 \ \ = short-hard gamma-ray burst + kilonova (EWs)
 \item[] Broad-band in gravitational waves: 10Hz - 2000Hz
 \item[] Ultra broad-band in electromagnetic waves: gamma rays to radio.
 \item A personal motivation, a simple question \\
{\small ``What can we offer to the astronomy community with future GW detections?''}
 \end{itemize}

@@

\begin{frame}{Gravitational waves: d.o.f.'s}
$A_{\mu\nu} $ is the polarization tensor.
\begin{itemize}
 \uncover<2->{\item $\{ \bar{h}_{\mu\nu}, A_{\mu\nu} \}$: $4\times4$, symmetric \uncover<3->{$\hspace{1.5cm}\Rightarrow \f{4\times 5}{2}\ \ \ = 10$ d.o.f.}}
 \uncover<4->{\item Gauge condition: $\nabla_\mu \bar{h}^{\mu\nu} =  A_{\mu\nu} k^\nu= 0$ \uncover<5->{$\Rightarrow10-4 = \, 6$ d.o.f.}}
 \uncover<6->{\item Residual gauge freedom \hspace{2.25cm} \uncover<7->{$\Rightarrow 6-4 \ \ = \alert{2}$ \alert{d.o.f.}}}
 %\uncover<7->{\vspace{2mm}\begin{center}$ \bar{h}'_{\mu\nu} = \bar{h}_{\mu\nu} - \xi_{\mu,\nu} - \xi_{\nu,\mu} + \eta_{\mu\nu} \nabla_\alpha \xi^\alpha . $ \end{center}\vspace{2mm}}
\end{itemize}
\uncover<7->{\quad \ Consistent with $\pm 2$ helicities of a \alert{massless} spin 2 boson.\\}
\uncover<8->{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): \uncover<10->{$\begin{array}{l}A_{xx}=-A_{yy} = h_\oplus  \\ A_{xy}=\ \ A_{yx} = h_\otimes  \\ \end{array}$}}

{\begin{center} \includegraphics[height=2.79875cm]{figs/white_box.png}\end{center}}
\end{frame}

\begin{frame}{Gravitational waves: d.o.f.'s}
%\begin{center}
%\animategraphics[loop,controls,width=3cm]{12}{GWs_frame-}{0}{29} 
%\end{center}
$A_{\mu\nu} $ is the polarization tensor.
\begin{itemize}
{\item $\{ \bar{h}_{\mu\nu}, A_{\mu\nu} \}$: $4\times4$, symmetric {$\hspace{1.5cm}\Rightarrow \f{4\times 5}{2}\ \ \ = 10$ d.o.f.}}
 {\item Gauge condition: $\nabla_\mu \bar{h}^{\mu\nu} =  A_{\mu\nu} k^\nu= 0${ $\Rightarrow10-4 = \,6$ d.o.f.}}
 {\item Residual gauge freedom \hspace{2.25cm}{ $\Rightarrow 6-4 \ \ = \alert{2}$ \alert{d.o.f.}}}
 %{\vspace{2mm}\begin{center}$ \bar{h}'_{\mu\nu} = \bar{h}_{\mu\nu} - \xi_{\mu,\nu} - \xi_{\nu,\mu} + \eta_{\mu\nu} \nabla_\alpha \xi^\alpha . $ \end{center}\vspace{2mm}}
\end{itemize}
{\quad \ Consistent with $\pm 2$ helicities of a \alert{massless} spin 2 boson.\\}
{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): {$\begin{array}{l}A_{xx}=-A_{yy} = h_\oplus  \\ A_{xy}=\ \ A_{yx} = h_\otimes  \\ \end{array}$}}
{\begin{center} \animategraphics[loop,controls,height=2.4cm]{12}{GWs_plus-}{0}{20} \hspace{1cm} \animategraphics[loop,controls,height=2.4cm]{12}{GWs_cross-}{0}{20}\end{center}}
\end{frame}

\begin{frame}{Making gravitational waves}{non-spherical, accelerated motion}
 \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\% (BICEP 2).\\
 \uncover<2->{Gravitational-wave luminosity: \uncover<3->{\alert{quadrupole} radiation}}
 \uncover<3->{\begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\\vspace{2mm}}
 \uncover<4->{\begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}}
 \uncover<5->{{\bf Binary systems:} 2 points masses in circular orbit. }

@@

\begin{frame}{Making gravitational waves}{non-spherical, accelerated motion}
 \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\%  (BICEP 2).\\
 Gravitational-wave luminosity: \alert{quadrupole} radiation
 \begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\ \vspace{2mm}
 \begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}
 {\bf Binary systems:} 2 points masses in circular orbit. \todo{Make $\dot{E}$s consistent}
 \begin{tikzpicture}[overlay,remember picture]
\onslide<5->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.8cm)}]current page.center) {\animategraphics[loop,controls,height=2.4cm]{12}{Circ_Orb-}{0}{20}};
\onslide<2->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-1.3cm)}]current page.center) {$M=m_1+m_2,\ x(t) = R \cos\Omega t, \ y(t) = R \sin\Omega t .$};
\onslide<3->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(3cm,-2.2cm)}]current page.center) {$ Q^{ij} =  2 M\, x^i x^j, \quad \boxed{\dot{E} = \f{128}{5}\f{G}{c^5} \Omega^6 M^2 R^4}$.};
\onslide<4->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2.5cm,-3.2cm)}]current page.center) {Enhancement due to \red{$e$} (Peters \& Mathews).};
\onslide<5->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-4cm)}]current page.center) {$ \dot{E} = \textcolor{red}{\f{\left(1 + \f{73}{24}e^2+ \f{37}{96} e^4 \right)}{(1-e^2)^{7/2}}} \f{32}{5}\f{G}{c^5}\f{M m_1^2 m_2^2}{a^5}.$};
\end{tikzpicture}
\end{frame}

 \begin{frame}{Binary Neutron Star Inspirals}

>>>>

\subtitle{\todo{Add background image}} % (optional)

@@

\begin{frame}{Outline}
\begin{itemize}
 \item Motivation
 \item Gravitational waves
 \item Binary neutron star inspirals
 \item Gravitational-wave detectors
 \item Event rates 
\end{itemize}
\todo{finish this slide remove later if short on time}

\begin{frame}{Motivation: Multi-messenger Astronomy}
\begin{itemize}
 \item \emph{Multi}: two fundamentally different waves from common events.
 \item[]\quad Gravitational waves (GWs): ``hearing''  the universe.
 \item[]\quad Electromagnetic waves (EWs): ``seeing'' the universe.
 \item \red{GW170817}-\bl{GRB170817A}-\textcolor{brown}{AT2017gfo}: the ``event'' \\
 \quad inspiral + merger of two neutron stars (GWs) \\
 \ \ = short-hard gamma-ray burst + kilonova (EWs)
 \item[] Broad-band in gravitational waves: 10Hz - 2000Hz
 \item[] Ultra broad-band in electromagnetic waves: gamma rays to radio.
 \item A simple question \\
{\small ``What can we offer to the astronomy community with future GW detections?''}
 \end{itemize}

@@

\begin{frame}{Gravitational waves: d.o.f.'s}
$A_{\mu\nu} $ is the polarization tensor.
\begin{itemize}
 \uncover<2->{\item $\{ \bar{h}_{\mu\nu}, A_{\mu\nu} \}$: $4\times4$, symmetric \uncover<3->{$\hspace{1.5cm}\Rightarrow \f{4\times 5}{2}\ \ \ = 10$ d.o.f.}}
 \uncover<4->{\item Gauge condition: $\nabla_\mu \bar{h}^{\mu\nu} =  A_{\mu\nu} k^\nu= 0$ \uncover<5->{$\Rightarrow10-4 = \, 6$ d.o.f.}}
 \uncover<6->{\item Residual gauge freedom \hspace{2.25cm} \uncover<7->{$\Rightarrow 6-4 \ \ = \alert{2}$ \alert{d.o.f.}}}
 %\uncover<7->{\vspace{2mm}\begin{center}$ \bar{h}'_{\mu\nu} = \bar{h}_{\mu\nu} - \xi_{\mu,\nu} - \xi_{\nu,\mu} + \eta_{\mu\nu} \nabla_\alpha \xi^\alpha . $ \end{center}\vspace{2mm}}
\end{itemize}
\uncover<7->{\quad \ Consistent with $\pm 2$ helicities of a \alert{massless} spin 2 boson.\\}
\uncover<8->{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): \uncover<10->{$\begin{array}{l}A_{xx}=-A_{yy} = h_\oplus  \\ A_{xy}=\ \ A_{yx} = h_\otimes  \\ \end{array}$}}
\\
\todo{Replace with Maggiore's discussion?}
{\begin{center} \includegraphics[height=2.79875cm]{figs/white_box.png}\end{center}}
\end{frame}

\begin{frame}{Gravitational waves: d.o.f.'s}
%\begin{center}
%\animategraphics[loop,controls,width=3cm]{12}{GWs_frame-}{0}{29} 
%\end{center}
$A_{\mu\nu} $ is the polarization tensor.
\begin{itemize}
{\item $\{ \bar{h}_{\mu\nu}, A_{\mu\nu} \}$: $4\times4$, symmetric {$\hspace{1.5cm}\Rightarrow \f{4\times 5}{2}\ \ \ = 10$ d.o.f.}}
 {\item Gauge condition: $\nabla_\mu \bar{h}^{\mu\nu} =  A_{\mu\nu} k^\nu= 0${ $\Rightarrow10-4 = \,6$ d.o.f.}}
 {\item Residual gauge freedom \hspace{2.25cm}{ $\Rightarrow 6-4 \ \ = \alert{2}$ \alert{d.o.f.}}}
 %{\vspace{2mm}\begin{center}$ \bar{h}'_{\mu\nu} = \bar{h}_{\mu\nu} - \xi_{\mu,\nu} - \xi_{\nu,\mu} + \eta_{\mu\nu} \nabla_\alpha \xi^\alpha . $ \end{center}\vspace{2mm}}
\end{itemize}
{\quad \ Consistent with $\pm 2$ helicities of a \alert{massless} spin 2 boson.\\}
{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): {$\begin{array}{l}A_{xx}=-A_{yy} = h_\oplus  \\ A_{xy}=\ \ A_{yx} = h_\otimes  \\ \end{array}$}}
\\
\todo{Replace with Maggiore's discussion?}
{\begin{center} \animategraphics[loop,controls,height=2.4cm]{12}{GWs_plus-}{0}{20} \hspace{1cm} \animategraphics[loop,controls,height=2.4cm]{12}{GWs_cross-}{0}{20}\end{center}}
\end{frame}

\begin{frame}{Making gravitational waves}{non-spherical, accelerated motion}
 \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\% (BICEP 2).\\
 \uncover<2->{Gravitational-wave luminosity: \uncover<3->{\alert{quadrupole} radiation}  (leading-order)}
 \uncover<3->{\begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\\vspace{2mm}}
 \uncover<4->{\begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}}
 \uncover<5->{{\bf Binary systems:} 2 points masses in circular orbit. }

@@

\begin{frame}{Making gravitational waves}{non-spherical, accelerated motion}
 \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\%  (BICEP 2).\\
 Gravitational-wave luminosity: \alert{quadrupole} radiation (leading-order)
 \begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\ \vspace{2mm}
 \begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}
 {\bf Binary systems:} 2 points masses in circular orbit.\todo{$R\to r$ in vid}
 \begin{tikzpicture}[overlay,remember picture]
\onslide<5->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.8cm)}]current page.center) {\animategraphics[loop,controls,height=2.4cm]{12}{Circ_Orb-}{0}{20}};
\onslide<2->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-1.3cm)}]current page.center) {$\mu=m_1 m_2/M^2,\ x(t) = r \cos\Omega t, \ y(t) = r \sin\Omega t $};
\onslide<3->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(2.25cm,-2.2cm)}]current page.center) {$ Q^{ij} =  2 M\, x^i x^j, \qquad \boxed{\dot{E} = \f{32}{5}\f{G\mu^2}{c^5}r^4 \Omega^6}$};
\onslide<4->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2.5cm,-3.2cm)}]current page.center) {Enhancement due to \bl{$e$} (Peters \& Mathews).};
\onslide<5->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-4cm)}]current page.center) {$ \bl{\f{\left(1 + \f{73}{24}e^2+ \f{37}{96} e^4 \right)}{(1-e^2)^{7/2}}}$};
\end{tikzpicture}
\end{frame}

 \begin{frame}{Binary Neutron Star Inspirals}
 Notation:
 \begin{itemize}
  \item $\red{f} $: GW frequency.
  \item $\omega\equiv2\pi f = 2\Omega$: GW angular frequency.
  \item $t$: observer/detector time \quad$ \Longrightarrow\quad\dot{Y}= dY/dt$.
 \end{itemize}

  Assumptions:
  \begin{itemize}
   \item Quasi-circular orbits: $e \ll 1$ and $\tfrac{|\dot{r}|}{r\Omega} <10^{-3} $ at $f=100\,$Hz.
   \item Point masses: tidal effects for $f \gtrsim 100\,$Hz
   \item Set $m_1 =m_2 = 1.4 M_\odot$, constraints: $1.2 M_\odot \lesssim m_\text{NS}\lesssim 1.6M_\odot$.
   \item Use Newtonian/post-Newtonian theory ($\le$3.5{\bf PN}).
   \item Terminate inspiral at Schwarzschild ISCO \todo{add ISCO curve?}
   \begin{footnotesize}
   \[f_\text{ISCO} = \f{c^3}{6^{3/2}\pi G M} \simeq 1571 \left(\f{2.8M_\odot}{M}\right)\text{Hz}\] 
   \end{footnotesize}
   \item Quadrupolar GWs only: higher modes suppressed by $\tfrac{m_1-m_2}{M}\tfrac{v^2}{c^2}$
   \item \todo{what about the 21 mode?}
   \item Neglect spins: spin-orbit $\tfrac{\dot{E}_\text{SO}}{\dot{E}} \sim \tfrac{v_s}{c}\tfrac{v}{c}\tfrac{R_\text{NS}}{r}$, spin-spin $\sim \tfrac{v^4}{c^4}$
  \end{itemize}

\begin{frame}{Binary Neutron Star Inspirals}{Newtonian evolution}
 Define \bl{chirp mass} \hspace{1.cm} $\red{M_c} \equiv \mu^{3/5} M^{2/5} = \tfrac{(m_1 m_2)^{3/5}}{(m_1+m_2)^{1/5}}$ \\
 %and symmetric mass ratio\qquad $\nu \equiv \tfrac{\mu}{M} =\tfrac{m_1 m_2}{M^2}$\\
 \vspace{1mm}
 which gives, using Kepler's \bl{third law}: $\Omega^2 = G M r^{-3}=\omega^2/4$   
 \begin{footnotesize}
  $$ \boxed{\dot{E} = \f{32}{5}\f{c^5}{G} \left(\f{G M_c\, \omega}{2c^3}\right)^{10/3}}$$
 \end{footnotesize}\\
%
{\bf Key idea:} \red{energy balance} between $\dot{E}$ and \\
$\tfrac{d}{dt}$ of gravitational binding energy
$ E_b= -\tfrac{G m_1 m_2}{2r} = -\left(\tfrac{G^2 M_c^5 \omega^2}{32}\right)^{1/3} $
%
\[ 
 \dot{E}(f) = -\dot{E}_b(f) \Longrightarrow \boxed{\red{\dot{f}} = \f{96}{5}\pi^{8/3} \f{(G M_c)}{c^5}^{5/3}\, \red{f^{11/3}} }
 \]
\[
 \red{ \dot{f} \propto f^{11/3}\quad(1)}
\]

\begin{tikzpicture}[overlay,remember picture]
\node[draw, red,thick,minimum width=3cm,minimum height=0.75cm] (b) at (5.9,0.85){};
\end{tikzpicture}

\begin{frame}{Binary Neutron Star Inspirals}{Inspiral time}
Integrate $\dot{f} \sim f^{11/3} \quad \Longrightarrow \quad \int dt \sim \int f^{-11/3}df \quad\Rightarrow\quad t \sim \red{f^{-8/3}}$
\\
\vspace{1mm}
Fix integration constant $\tau = t_\text{coal} - t >0$. \\
\vspace{2mm}
Introduce \red{inspiral time}, i.e, time to BNS \bl{coal}escence
%
\begin{align}
 \red{\tau_\text{insp}(f)} &= \f{5}{256\pi}\f{c^5}{(\pi G M_c)^{5/3}} \,{f^{-8/3}}\nn\\
 &\simeq \red{16.72\,\text{minutes}} \, \left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\,\red{\left(\f{10\,\text{Hz}}{f}\right)^{8/3}\quad(2)}\nn
\end{align}
Number of GW cycles to coalescence: $\int \tfrac{f}{\dot{f}}df\sim f^{-5/3}$ %$\int df {f}/\dot{f}$
\begin{align}
 \red{\mathcal{N}_\text{cyc}(f)} %&=\f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\left[ f^{-5/3}-f_\text{max}^{-5/3}\right]\nn \\
 &\approx 1.605\times \red{10^4 \left(\f{10\,\text{Hz}}{f} \right)^{5/3}}\,\left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\quad \red{(3)}\nn
\end{align}

\begin{tikzpicture}[overlay,remember picture]
\node[draw, red,thick,minimum width=8.2cm,minimum height=1.3cm] (b) at (7.,3.35){};
\node[draw, red,thick,minimum width=10cm,minimum height=1.3cm] (b) at (6.2,1){};
\end{tikzpicture}
